### 2023-01-12 RR-9418.tex
last update for RR

\documentclass[twoside]{article}

@@

\RRnote{\TODO{This preprint has not undergone peer review (when
    applicable) or any post-submission improvements or
    corrections. The Version of Record of this contribution is
    published in [insert volume title], and is available online at
    https://doi.org/[insert DOI]}}

@@

\input{input/introduction.tex}
\input{input/background.tex}
\input{input/proposal.tex}
\input{input/experiments.tex}
\input{input/related_work.tex}
\input{input/conclusion.tex}
%% \input{input/acknowledgment.tex}

>>>>

\documentclass{article}

@@

\RRnote{This preprint has not undergone peer review or any
  post-submission improvements or corrections. The Version of Record
  of this contribution is published in \emph{Algorithms and
  Architectures for Parallel Processing (LNCS volume 13777)}, and is
  available online at
  \url{https://doi.org/10.1007/978-3-031-22677-9_23}}

@@

\input{input/introduction.tex}
\input{input/background.tex}
\input{input/proposal.tex}
\input{input/experiments.tex}
\input{input/related_work.tex}
\input{input/conclusion.tex}
\input{input/acknowledgements.tex}
